---
title: "Second wave of COVID-19 in Switzerland"
author: "Nicolly Oliveira"
date: "today"
format: 
  html:
    toc: true
    toc-location: body 
    code-fold: show
    code-tools: true
    df-print: paged
    embed-resources: true
  pdf: 
    toc: true
  docx: 
    toc: true
editor_options: 
  chunk_output_type: inline
---

```{r}
#| output: false
# Load libraries
library(here)
library(tidyverse)
library(lubridate)
install.packages("unibeCols", repos = "https://ctu-bern.r-universe.dev")
library(unibeCols)
```

## Introduction

The aim of this exercise is to visualize the increase in laboratory-confirmed cases of COVID-19 in Switzerland during autumn 2020.

## Data

We read and process the data of laboratory-confirmed cases of COVID-19 in Switzerland as reported by the \[Federal Office of Public Health\] (https://idd.bag.admin.ch/).

```{r}
#| output: false
# Read data
cases <- read_csv("https://ispmbern.github.io/projects-in-R/data/raw/COVID19Cases_geoRegion.csv")
```

```{r}
# Process data
region <- "CH"
window_start <- ymd("2020-09-01")
window_end <- ymd("2020-11-30")
cases <- cases |>
  filter(geoRegion == region & datum >=
           window_start & datum <= window_end) |>
  select(datum, entries)
cases
```

@Figure1 The figure shows the number of laboratory-confirmed cases of COVID-19 in Switzerland from `r window_start`to `r window_end`.

```{r}
#| label: fig-cases
#| fig-cap: "Laboratory-confirmed cases of COVID-19 in Switzerland in 2020."
#| fig-width: 8
#| fig-height: 4
ggplot(cases, aes(x=datum, y=entries)) +
  geom_bar(stat = "identity", fill=unibeSaphire()) +
  labs(x="", y="Laboratory-confirmed cases") +
  theme_minimal()
```

## Conclusions

The number of laboratory-confirmed cases of COVID-19 in Switzerland rapidly increased during October 2020 and subsequently declined.


